Paper_analyses

### 2022-02-07 Old scripts/pupil_arousal_datarmd.Rmd
07 Jan return

db_full4new_stim_screen_pupil_nopract_nt %>%
  group_by(ssid,mediansplit_sample_valence2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal_c, BIO_CDA.PhasicMax_z, color =mediansplit_sample_valence2))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

@@

pupil_arousal_findings$arousal_scr <- lmer(BIO_CDA.PhasicMax_z ~ valence_c +(1|ssid),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt,
                                      pp_arousal_outler == FALSE))
                                      # mediansplit_self_valence == "More positive"))

>>>>

db_full4new_stim_screen_pupil_nopract_nt %>%
  group_by(ssid,mediansplit_sample_valence2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal_c, BIO_CDA.PhasicMax_z))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

@@

pupil_arousal_findings$arousal_scr <- lmer(BIO_CDA.PhasicMax_z ~ valence_c + (1|ssid),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt,
                                      pp_arousal_outler == FALSE))
                                      # mediansplit_self_valence == "More positive"))

### 2022-02-07 Paper_Analyses_subj_obje_arousal.Rmd
07 Jan return

# create and empty dataframe for the timecourse analyses
timecourse_60bin_result_df <- data.frame(timebins= rep(NA, 60), 
                                       Estimate_ar= rep(NA, 60), 
                                       t_ar=rep(NA, 60), 
                                       p_ar=rep(NA, 60),
                                       Estimate_vl= rep(NA, 60), 
                                       t_vl=rep(NA, 60), 
                                       p_vl=rep(NA, 60),
                                       Estimate_br= rep(NA, 60), 
                                       t_br=rep(NA, 60), 
                                       p_br=rep(NA, 60),
                                       Estimate_ar_vl= rep(NA, 60), 
                                       t_ar_vl=rep(NA, 60), 
                                       p_ar_vl=rep(NA, 60),
                                       cov= as.character(rep(NA,60)))

@@

```{r}
library(tidyverse)
db_full6new_hr_fix_stim_nt1.1

clustering<- db_full6new_hr_fix_stim_nt1.1%>%
  subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  select(
                    c(Bio_Mean_HR_dif, pup_basCor, BIO_CDA.PhasicMax, BIO_CDA.ISCR, BIO_TTP.AmpSum,
                      BIO_CDA.SCR, arousal, valence, ArousalMean, ValenceMean, stimIAPS, tNo, TAS, AQ, Age,
                      gender, ssid, stimDescription, fix_count, mean_fix_dur))

@@

View(db_full6new_hr_fix_stim_select2_NT_no_outl_5)
db_forBADA1<- data.table::dcast(setDT(db_full6new_hr_fix_stim_select2_NT_no_outl_5), 
                    ssid + TAS+AQ+Group ~ stimIAPS2, value.var = c('pup_basCor',
                'Bio_Mean_HR_dif', 'log1p_BIO_CDA.PhasicMax', 'arousal', 'valence'))

@@

var.data <- all.data3_forPCA[,c(4:171)]

@@

# inferential PCA
var.PCA.scr_hr_pup <-InPosition::epPCA.inference.battery(var.data, 
                                       scale = TRUE, 
                                       center = TRUE, 
                                       # DESIGN = var.design_asd, 
                                       # make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)

@@

@@

library(InPosition)
var.PCA.scr_hr_pup_val <-InPosition::epPCA.inference.battery(all.data3_forPCA_withval[,4:226], 
                                       scale = TRUE, 
                                       center = TRUE, 
                                       # DESIGN = var.design_asd, 
                                       # make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)

@@

clustering_new_pre_PCA_2$stimDescription
res.mfa <- MFA(clustering_new_pre_PCA_2, 
               group = c(2, 1, 1, 1, 2, 1), 
               type = c("n", "s", "s", "s", "s", "s"),
               name.group = c("pp_stim","pupil","HR","SCR", "ar_val","fix"),
               num.group.sup = c(1,2),
               graph = TRUE)

@@

```
```{r}
library("factoextra")
eig.val <- get_eigenvalue(res.mfa)
head(eig.val)

@@

the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
```{r}
fviz_screeplot(res.mfa)

@@

```
```{r}
# Coordinates
head(quanti.var$coord)
# Cos2: quality on the factore map
head(quanti.var$cos2)
# Contributions to the dimensions
head(quanti.var$contrib)

@@

```
```{r}

@@

@@

```
```{r}
library("factoextra")
eig.val_agg <- get_eigenvalue(res.mfa_agg)
head(eig.val_agg)

>>>>

# create and empty dataframe for the timecourse analyses

timecourse_60bin_result_df_bp<- timecourse_60bin_result_df

timecourse_60bin_result_df <- data.frame(timebins= rep(NA, 60), 
                                       Estimate_ar= rep(NA, 60), 
                                       t_ar=rep(NA, 60), 
                                       p_ar=rep(NA, 60),
                                       Estimate_vl= rep(NA, 60), 
                                       t_vl=rep(NA, 60), 
                                       p_vl=rep(NA, 60),
                                       Estimate_br= rep(NA, 60), 
                                       t_br=rep(NA, 60), 
                                       p_br=rep(NA, 60),
                                       Estimate_ar_vl= rep(NA, 60), 
                                       t_ar_vl=rep(NA, 60), 
                                       p_ar_vl=rep(NA, 60),
                                       cov= as.character(rep(NA,60)))

@@

```{r}
library(tidyverse)
db_full6new_hr_fix_stim_nt1.1
View(clustering)
clustering<- db_full6new_hr_fix_stim_nt1.1%>%
  subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  select(
                    c(Bio_Mean_HR_dif, pup_basCor, BIO_CDA.PhasicMax, BIO_CDA.ISCR, BIO_TTP.AmpSum,
                      BIO_CDA.SCR, arousal, valence, ArousalMean, ValenceMean, stimIAPS, tNo, TAS, AQ, Age,
                      gender, ssid, stimDescription, fix_count, mean_fix_dur))

@@

View(db_full6new_hr_fix_stim_select2_NT_no_outl_5)
View(db_forBADA1)
db_forBADA1<- data.table::dcast(setDT(db_full6new_hr_fix_stim_select2_NT_no_outl_5), 
                    ssid + TAS+AQ+Group ~ stimIAPS2, value.var = c('pup_basCor',
                'Bio_Mean_HR_dif', 'log1p_BIO_CDA.PhasicMax', 'arousal', 'valence'))

View(db_forBADA)

@@

View(all.data3_forPCA)
var.data <- all.data3_forPCA[,c(4:171)]

@@

View(var.data)
# inferential PCA
var.PCA.scr_hr_pup <-InPosition::epPCA.inference.battery(var.data, 
                                       scale = TRUE, 
                                       center = TRUE, 
                                       # DESIGN = var.design_asd, 
                                       # make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)

@@

# mySpca <- spca(obj, ask=FALSE, type=1, scannf=FALSE)
# install.packages("adegenet")
library(adegenet)
# install.packages('spdep')
install.packages("sf")
library(spdep)

mySpca <- spca(obj, ask=FALSE, type=1, scannf=FALSE)
?spca
mySpca <- spca(var.data, ask=FALSE, type=1, scannf=FALSE)

install.packages("cpca")

?cpca::cpc()

var.data$sid <- all.data3_forPCA$ssid
require("plyr")
require("abind")

daply(var.data, "sid", function(x) cov(x[, -ncol(x)]))
C <- aperm(C, c(2, 3, 1)) # put the 1st dimension to the end
dim(C)
dimnames(C)

mod <- cpc(C)
str(mod)

round(mod$CPC, 2)

pca::cpc(var.data, method = "stepwise", k = 2)

@@

library(InPosition)

```{r}
var.PCA.scr_hr_pup_val <-InPosition::epPCA.inference.battery(all.data3_forPCA_withval[,4:226], 
                                       scale = TRUE, 
                                       center = TRUE, 
                                       # DESIGN = var.design_asd, 
                                       # make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)

View(clustering_new_pre_PCA)

# start by creating a cluster within self reports
?cut
clustering_new_pre_PCA$arousal_3cat <- cut(clustering_new_pre_PCA$arousal, 3, labels = c("low", "mid", "high"))

colnames(clustering_new_pre_PCA)

var.design_ar = as.factor(clustering_new_pre_PCA$arousal_3cat)

library(prettyGraphs)
library(InPosition)

View(clustering_new_pre_PCA)
clustering_new_pre_PCA[,6:8]

clustering_new_pre_PCA1<- subset(clustering_new_pre_PCA,
                                 !is.na(pup_basCor))

var.design_ar = as.factor(clustering_new_pre_PCA1$arousal_3cat)
 table(is.na(var.design_ar))

 clustering_new_pre_PCA2<- subset(clustering_new_pre_PCA1, !is.na(arousal_3cat))

 var.design_ar<- c(clustering_new_pre_PCA2$arousal_3cat)

 clustering_new_pre_PCA2$arousal_3cat <- cut(clustering_new_pre_PCA2$arousal, 2,
                                            labels = c("low", "high"))

# ExPosition:
 ?TInPosition::tepBADA.inference.battery
var.bada.ar_physio <- TInPosition::tepBADA.inference.battery(clustering_new_pre_PCA2[,6:8], 
                                                       scale = FALSE, 
                                                       center = FALSE, 
                                                       # DESIGN = factor( clustering_new_pre_PCA2$arousal_3cat ),
                                                        DESIGN = factor(var.design_ar ),
                                                       make_design_nominal = TRUE,
                                                       group.masses = NULL, 
                                                       weights = NULL, 
                                                       graphs = TRUE, 
                                                       k = 2, 
                                                       test.iters = 100, 
                                                       critical.value = 2)

var.bada.ar_physio[["Fixed.Data"]][["TExPosition.Data"]][["fii"]][,1]

clustering_new_pre_PCA2$test_pc1<-var.bada.ar_physio[["Fixed.Data"]][["TExPosition.Data"]][["fii"]][,1]

clustering_new_pre_PCA2%>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(arousal> -6)%>%
  ggplot(aes(valence, test_pc1 ))+
  geom_point()+
  ggpubr::stat_cor()+
  geom_smooth(method = 'lm')
  xlim(-6,3.2)

  # get ground truth data
clustering_new_pre_PCA2

colnames(db_full4new_stim_screen_pupil_nopract)

stimIapsval<- db_full4new_stim_screen_pupil_nopract %>%
  group_by(stimIAPS2)%>%
  summarise_at(c("ValenceMean", "ArousalMean"), mean, na.rm = TRUE)

clustering_new_pre_PCA3 <- left_join(clustering_new_pre_PCA2, stimIapsval)

clustering_new_pre_PCA3$arousal_3cat_ground<- cut(clustering_new_pre_PCA3$ArousalMean,3, labels = 
                                                    c("low", "mid", "high"))

#

var.design_ar_2<- factor(clustering_new_pre_PCA3$arousal_3cat_ground )

table(is.na( var.design_ar_2))
# sum(var.design_ar_2)
# TExPosition::tepBADA()
var.bada.ar_physio2 <- TInPosition::tepBADA.inference.battery(clustering_new_pre_PCA3[,6:8], 
                                                       scale = TRUE, 
                                                       center = TRUE, 
                                                       # DESIGN = factor( clustering_new_pre_PCA2$arousal_3cat ),
                                                        DESIGN = var.design_ar_2,
                                                       make_design_nominal = TRUE,
                                                       group.masses = NULL, 
                                                       weights = NULL, 
                                                       graphs = TRUE, 
                                                       k = 2, 
                                                       test.iters = 100, 
                                                       critical.value = 2)

# do with valence

clustering_new_pre_PCA3$arousal_3cat<- cut(clustering_new_pre_PCA3$valence,3, labels = 
                                                    c("neg", "mid", "pos"))

#

var.design_ar_2<- factor(clustering_new_pre_PCA3$arousal_3cat_ground )

table(is.na( var.design_ar_2))
# sum(var.design_ar_2)
# TExPosition::tepBADA()
var.bada.vl_physio3 <- TInPosition::tepBADA.inference.battery(clustering_new_pre_PCA3[,6:8], 
                                                       scale = TRUE, 
                                                       center = TRUE, 
                                                       # DESIGN = factor( clustering_new_pre_PCA2$arousal_3cat ),
                                                        DESIGN = factor(clustering_new_pre_PCA3$arousal_3cat),
                                                       make_design_nominal = TRUE,
                                                       group.masses = NULL, 
                                                       weights = NULL, 
                                                       graphs = TRUE, 
                                                       k = 2, 
                                                       test.iters = 100, 
                                                       critical.value = 2)

clustering_new_pre_PCA3$vall_3_gr<- cut(clustering_new_pre_PCA3$ValenceMean,3, labels = 
                                                    c("neg", "mid", "pos"))

table(is.na( var.design_ar_2))
# sum(var.design_ar_2)
# TExPosition::tepBADA()
var.bada.vlgr_physio4 <- TInPosition::tepBADA.inference.battery(clustering_new_pre_PCA3[,6:8], 
                                                       scale = TRUE, 
                                                       center = TRUE, 
                                                       # DESIGN = factor( clustering_new_pre_PCA2$arousal_3cat ),
                                                        DESIGN = factor(clustering_new_pre_PCA3$vall_3_gr),
                                                       make_design_nominal = TRUE,
                                                       group.masses = NULL, 
                                                       weights = NULL, 
                                                       graphs = TRUE, 
                                                       k = 2, 
                                                       test.iters = 100, 
                                                       critical.value = 2)

# MFA

res.mfa <- MFA(clustering_new_pre_PCA_2, 
               group = c(2, 1, 1, 1), 
               type = c("n", "s", "s", "s"),
               name.group = c("pp_stim","pupil","HR","SCR"),
               # num.group.sup = c(1,2),
               graph = TRUE)

colnames(clustering_new_pre_PCA3)

clustering_new_pre_PCA3$arousal_3cat<- cut(clustering_new_pre_PCA3$arousal,3, labels = 
                                                    c("low", "mid", "high"))
c<-FactoMineR::MFA(clustering_new_pre_PCA3[,c(1,14,6:8)], 
               group = c(2, 1, 1, 1), 
               type = c("n", "s", "s", "s"),
               name.group = c("pp_stim","pupil","HR","SCR"),
               num.group.sup = c(1,2),
               graph = TRUE)

?FactoMineR::MFA
FactoMineR::MFA(clustering_new_pre_PCA3[,c(1,4,6:8,9,10)], 
               group = c(2, 1, 1, 1,1,1), 
               type = c("n", "s", "s", "s", "s", "s"),
               name.group = c("pp_stim","pupil","HR","SCR", "arousal", "valence"),
               num.group.sup = c(1,2),
               graph = TRUE)

# valence and arousal are creatign a strign compoent one maybe vecause of thir correlatipn
# so below I am droping one to see if we have more coherence
# ?
FactoMineR::MFA(clustering_new_pre_PCA3[,c(1,4,6:8,9)], 
               group = c(2, 1, 1, 1,1), 
               type = c("n", "s", "s", "s", "s"),
               name.group = c("pp_stim","pupil","HR","SCR", "arousal"),
               num.group.sup = c(1,2),
               ind.sup = c(1,2),
               graph = TRUE)

# include 
colnames(clustering_new_pre_PCA3)
unique(clustering_new_pre_PCA3$stimDescription)

clustering_new_pre_PCA3.1<- clustering_new_pre_PCA3[,c(1,4,6,7,8,9,10)]
res.mfa_bio_vs_self<- FactoMineR::MFA(clustering_new_pre_PCA3.1, 
               group = c(2, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

```{r}
# use stim as indicator
colnames(clustering_new_pre_PCA3)
clustering_new_pre_PCA3.1<- clustering_new_pre_PCA3[,c(1,5,6,7,8,9,10)]

res.mfa_bio_vs_self2<- FactoMineR::MFA(clustering_new_pre_PCA3.1[,2:7], 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

# now z score within participant
clustering_new_pre_PCA3.1.scale<- clustering_new_pre_PCA3.1%>%
  group_by(ssid)%>%
  mutate_if(is.numeric, scale)

clustering_new_pre_PCA3.1.scale$stim_descr
res.mfa_bio_vs_self2_scale<- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale[,2:7], 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

# Now try HMFA

library(FactoMineR)
??HMFA

H_n<- clustering_new_pre_PCA3.1.scale%>%
  group_by(ssid)%>%
  mutate(n = n())%>%
  summarise_at(c("n"), mean, na.rm = TRUE)

H_n.1<- H_n$n

as.list(H_n.1)
c(H_n.1)

hierar<- list(c(H_n.1))

View(wine)
FactoMineR::HMFA(clustering_new_pre_PCA3.1.scale[,2:7],
                 H = hierar, 
               # group = c(1, 3, 2), 
               type = c("n", "s", "s",  "s", "s",  "s"),
               # "s", "s", "s"
               name.group = c("pp_stim","auton","subj"),
               # num.group.sup = c(1),
                 # ncp = 
               # ind.sup = c(1,2),
               graph = TRUE)

# okay try and aggregate  response per stimuli

clustering_new_pre_PCA3.1.scale_agg_bystim<- clustering_new_pre_PCA3.1%>%
  group_by(stimDescription)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg<- clustering_new_pre_PCA3.1.scale_agg_bystim%>%
  mutate_if(is.numeric, scale)

res.mfa_bio_vs_self2_scale_aggbystim<- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_agg_bystim, 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

```{r}
res.mfa_bio_vs_self2_scale_afteraggbystim<- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg, 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

# agg by pp

```{r}
clustering_new_pre_PCA3.1.scale_agg_bysid<- clustering_new_pre_PCA3.1%>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

clustering_new_pre_PCA3.1.scale_aft_agg_bysid<- clustering_new_pre_PCA3.1.scale_agg_bysid%>%
  mutate_if(is.numeric, scale)

 FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_agg_bysid, 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

# now keep participant just cast pupil etc
clustering_new_pre_PCA3.1.scale

# dcast

library(data.table)

colnames(clustering_new_pre_PCA3.1.scale)
clustering_new_pre_PCA3.1.scale$pup_basCor<- clustering_new_pre_PCA3.1.scale$pup_basCor[,1]

clustering_new_pre_PCA3.1.scale$Bio_Mean_HR_dif<- clustering_new_pre_PCA3.1.scale$Bio_Mean_HR_dif[,1]

clustering_new_pre_PCA3.1.scale$log_BIO_CDA.PhasicMax<- clustering_new_pre_PCA3.1.scale$log_BIO_CDA.PhasicMax[,1]

clustering_new_pre_PCA3.1.scale$arousal<- clustering_new_pre_PCA3.1.scale$arousal[,1]

clustering_new_pre_PCA3.1.scale$valence<- clustering_new_pre_PCA3.1.scale$valence[,1]

clustering_new_pre_PCA3.1.scale_dcast<- data.table::dcast(setDT(clustering_new_pre_PCA3.1.scale), 
                    ssid  ~ stimDescription, 
                    value.var = c('pup_basCor',
                'Bio_Mean_HR_dif', 'log_BIO_CDA.PhasicMax', 'arousal','valence'), fun.aggregate = mean)

colnames(clustering_new_pre_PCA3.1.scale_dcast)

res.mfadcast <- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_dcast[,
                                                                      2:ncol(clustering_new_pre_PCA3.1.scale_dcast)], 
               group = c(52, 52, 52, 52, 52), 
               type = c("s", "s", "s", "s", "s"),
               # "s", "s", "s"
               name.group = c("pup","hr", "scr", "ar", "vl"),
               # num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

53-2 #pupil

@@

View(clustering_new_pre_PCA_2)
clustering_new_pre_PCA_2$stimDescription
colnames(clustering_new_pre_PCA_2)

res.mfa <- MFA(clustering_new_pre_PCA_2, 
               group = c(2, 1, 1, 1), 
               type = c("n", "s", "s", "s"),
               name.group = c("pp_stim","pupil","HR","SCR"),
               # num.group.sup = c(1,2),
               graph = TRUE)

@@

```{r}
library("factoextra")
eig.val <- get_eigenvalue(res.mfa)
head(eig.val)

@@

the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
```{r}
library(FactoMineR)
library(factoextra)
??fviz_screeplot
fviz_screeplot(res.mfa)

@@

```{r}
# Coordinates
head(quanti.var$coord)
# Cos2: quality on the factore map
head(quanti.var$cos2)
# Contributions to the dimensions
head(quanti.var$contrib)

@@

@@

testget<-get_mfa(
  res.mfa,
  element = c("ind"))

clustering_new_pre_PCA3$getindaxis<- testget[["coord"]][,1]
clustering_new_pre_PCA3$getindaxis2<- testget[["coord"]][,2]

clustering_new_pre_PCA3%>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal, getindaxis))+
  geom_point()+
  ggpubr::stat_cor()+
  xlim(-,3.3)

clustering_new_pre_PCA3%>%
  group_by(ssid, arousal_3cat)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal, getindaxis2))+
  geom_point()+
  ggpubr::stat_cor()+
  facet_grid(~arousal_3cat)
  # xlim(-,3.3)

@@

```{r}
library("factoextra")
eig.val_agg <- get_eigenvalue(res.mfa_agg)
head(eig.val_agg)
